\begin{rSection}{Experience}
	\begin{jobListing}
    {University of Pittsburgh (Computer Science Dept.)}
    {Spring 2022 – Present}
    {Part-Time Instructor/Teaching Assistant}
    {Pittsburgh, PA}
		\begin{itemize}
			\item Led recitations in two core-level required courses (\textit{System Software} \& \textit{Discrete Structures}) to over 400 undergraduate students.
			\item Developed various course materials using x86 assembly and the C programming language.
			\item Provided comprehensive one-on-one academic support to students in office hours; performed grading duties.
		\end{itemize}
	\end{jobListing}
	
	\begin{jobListing}
    {Ansys, Inc (Digital Twins Team)}
    {May 2024 – August 2024}
    {Software Engineering Intern}
    {Pittsburgh, PA}
		\begin{itemize}
			\item Upgraded Azure CI/CD build pipelines to automatically publish nightly stable builds of the new Ansys TwinAI product; added new support for generating and collecting coverage reports to improve code quality.
			\item Implemented a container-based scripting library for reduced order model creation, allowing customers to integrate TwinAI into other products and use TwinAI in headless mode.
			\item Designed a tool for automatically generating CycloneDx Software Bill of Materials for C++ packages, satisfying government regulations and secure software requirements.
		\end{itemize}
	\end{jobListing}
	
	\begin{jobListing}
    {University of Pittsburgh (Swigonova Lab)}
    {March 2022–December 2023}
    {Lead Developer}
    {Pittsburgh, PA}
		\begin{itemize}
			\item Created a free and open-source library of various 3D macromolecular models and viewers to be used in the classroom.
			\item Using various open-source libraries and tools, created the front-end for the web page that displays each model and accompanying information sheet in the browser (\href{https://touchtheinvisible.com}{\nolinkurl{touchtheinvisible.com}})
			\item Created an easy-to-use content management system that allows non-technical lab members to easily manage and edit the website and its assets.
		\end{itemize}
	\end{jobListing}	
\end{rSection}