\begin{rSection}{Projects}
    \href{https://github.com/shinwookim/GRASP-HPO/}{\textbf{GRASP-HPO: Hyperparameter Optimization using Greedy Randomized Adaptive Search Procedure}}
    \\
    Working with Prof. Daniel Mosse, created a novel algorithm that can be used to find optimal hyperparameters when using various Machine Learning methods (e.g., XGBoost). Implemented the algorithm in Python and compared performance against other HPO algorithms in a real-world scenario of electrical substation intrusion detection systems (IDS).
    \begin{itemize}\vspace{-0.25em}
        \item Technologies Used: \textit{Python, scikit-learn, Ray, BOHB, HyperBand, HyperOpt}
    \end{itemize}

    \textbf{Adaptive Speculative Decoding: Improving Large Language Model Performance.}
    \\
    Working with Dr. Stephen Lee, developed an adaptive framework that can speed-up Large Language Model (LLM) inference by dynamically selecting appropriate draft model to use for speculative decoding.
    \begin{itemize}\vspace{-0.25em}
        \item Technologies Used: \textit{Python, Transformers, PyTorch, CUDA}
    \end{itemize}

    \textbf{Distributed Crash-Tolerant Key-Value Datastore using Consensus-based Protocols.}\\
    {Implemented a distributed data store server that can manage replicas using either an automated leader-election, or leaderless quorum mechanism.}
    \begin{itemize}\vspace{-0.25em}
        \item Technologies Used: \textit{Python, Zookeeper, gRPC, Kazoo, Docker}
    \end{itemize}


\end{rSection}
